Verifying Demonstrations

### 2019-02-27 paper/timestamp.tex

We require a few additional properties from \(\TS\) that are already provided by blockchains.
First, \(\TS\) must be continuously extended, such as in Bitcoin in which blocks are created every 10 minutes on average.
Second, \(\TS\) must provide \emph{immutability} and availability to any data committed through \(\TSstamp\) to ensure verifiability of the data by anyone at any time.
Note that thanks to \(\TS\) immutability, once a user has committed their data, that user only need to store some confirmation value instead of the data itself.
For instance, in the case of a blockchain, it would be sufficient for a user to only store both the hash of the block containing their participation proof and the hash of the proof.

>>>>

We require a few additional properties from \(\TS\) that are already provided by blockchains.
First, \(\TS\) must be continuously extended, such as in Bitcoin in which blocks are created every 10 minutes on average.
Second, \(\TS\) must provide \emph{immutability} and availability to any data committed through \(\TSstamp\) to ensure verifiability of the data by anyone at any time.

### 2019-02-27 paper/verifiability-analysis.tex

\Cref{CountOnce} is required to prevent Sybil attacks, in the sense
that Alice cannot provide two (or more) participation proofs for a
specific protest and thus be counted more than once.
To do this she must create more than one pseudonym, \(\pid\).
Indeed to be counted twice, Alice must produce a \(\pid'\neq \pid\).
Due to the deterministic property of \(\ACprf\), Alice must produce a new key 
\(\sk_P'\) such that the verifier\footnote{%
  Here the verifier is either the witness during the distance bounding or the 
  verifier who tries to verify the count.
} accepts the proof
\begin{multline*}
\PK\mleft\{ (\sk_P') : \pid' = \ACprf[_{\sk_P'}][\cid] \quad \land \mright. \\
    \sigma_P'' = \mleft. \ACblind[\ACsign[_{\ssk}][\sk_P']] \mright\}
\end{multline*}
while she does not know a valid signature on \(\sk_P'\).
As a consequence, this is reduced to the security of the \(\AC\) scheme and how 
often Alice can get a valid signature on a secret key from the \ac{CA} --- by 
assumption the \ac{CA} will issue only one signature for such a key, but she 
can try to illicitly use someone else's key.

@@

\Cref{SpatiallyRelated} is achieved by having a witness vouch anonymously that Alice was indeed at the location when the proof share was created.
To realize this, we must ensure that Alice cannot forge witness signatures.

In the trust-free case (see \cref{ProtocolVerification}), this is realized by 
using the same linkability mechanism as above.
\Ie to forge a witness signature, Alice must produce a \(\wid'\) such that
\begin{multline*}
  \pi_{\wid'}\gets \SPK\left\{ (\sk_W') : \right. \\
    \begin{aligned}
      \wid' &= \ACprf[_{\sk_W'}][\pid] \quad \land \\
      \sigma_W'' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W']] \right\}
    \end{aligned} \\
      (\pid, \wid', t_s, t_s', l),
\end{multline*}
is accepted by the verifier while not knowing a signature on the secret key 
\(\sk_W'\).
Thus, she must break the \(\AC\) scheme to succeed or get a valid signature on \(\sk_W'\) from the \ac{CA}.
As above, the latter could be done if she can find people willing to collude, 
or whose keys she illicitly can use anyway, or 
simply request new keys from the \ac{CA}.

% We assumed that Alice cannot collude with more than a threshold \(\theta\) of 
% witnesses.
% Thus, setting the threshold of at least \(\theta+1\) will prevent Alice from 
% cheating.
% (Note that Alice can produce \emph{one} witness signature for herself, since 
% she has access to her own \(\sk_P\), but no more.
% Thus, \(\theta > 1\) is a requirement in the trust-free case.)

The strength function from \cref{DefParticipationCount} ensures that
Alice either has to collude with \(\theta - 1\) witnesses (she can
produce \emph{one} witness signature for herself, since she has access
to her own \(\sk_P\), but no more) or, in the trusted witness case,
that Alice must be able to forge statements, \eg digital signatures,
from at least one witness that the verifier trusts.

>>>>

\Cref{CountOnce} prevents Sybil attacks, in the sense
that Alice cannot provide two (or more) participation proofs for a
specific protest and thus be counted more than once.
To do this she must create more than one pseudonym, \(\pid\).
Indeed, to be counted twice, Alice must produce a \(\pid'\neq \pid\).
Due to the deterministic property of \(\ACprf\), Alice must produce a new key 
\(\sk_P'\) such that the verifier\footnote{%
  Here the verifier is either the witness during the distance bounding or the 
  verifier who tries to verify the count.
} accepts the proof
\begin{multline*}
\PK\mleft\{ (\sk_P') : \pid' = \ACprf[_{\sk_P'}][\cid] \quad \land \mright. \\
    \sigma_P'' = \mleft. \ACblind[\ACsign[_{\ssk}][\sk_P']] \mright\}
\end{multline*}
while she does not know a valid signature on \(\sk_P'\).
As a consequence, this is reduced to the security of the \(\AC\) scheme.
Remember, by assumption the \ac{CA} will issue only one signature for such a 
key, so Alice cannot ask for a second one.

@@

\Cref{SpatiallyRelated} is achieved by having a witness vouch that Alice was 
indeed at the location when the proof share was created.
In essence, the witness performs distance bounding to ensure Alice is close to 
them, this is then propagated to the verifier through the signature and trust 
in the witness's honesty.
Alice has three options:
\begin{enumerate*}
\item\label{spatial-DF} relay her communication with an honest witness through 
  a conspirator,
\item\label{spatial-forge} forge a witness signature for the proof,
\item corrupt a witness to issue a proof although neither might be present at 
  the location.
\end{enumerate*}

Relaying the communication is \iac{DBDF} attack against the \ac{DB} protocol.
We assumed \ac{DBDF} resistance for the \ac{DB} protocol, so Alice cannot 
succeed with more than negligible probability.

Forging a witness's signature on a proof is equivalent to breaking linkability 
above (\cref{analysis-linkability}).
As above, this is reduced to the security of the \(\AC\) scheme.

Finally, in the case of trusted witnesses, Alice's chance of corrupting 
witnesses is reduced to the trustworthiness of the witnesses chosen by the 
verifier.
In the \(\theta\)-threshold case, with unknown witnesses, (by assumption) Alice 
succeeds only if she can corrupt at least \(\theta\) witnesses.

We note that the strength function from \cref{DefParticipationCount} allows the 
verifier to take different approaches, each of which must be individually 
analyzed.
In all of these cases, it is up to the verifier to perform a risk analysis.
